Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-30 manuscript/supplemental_material.Rnw
fix some of the missing project numbers

\documentclass[english,12pt]{article}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{wrapfig}
% \usepackage{txfonts}
\usepackage{acronym}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage[backend=biber,natbib=true,hyperref=true,style=reading,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads,nofighead,notabhead]{endfloat}
% \AtBeginFigures{\section*{Figure Legends}\renewcommand{\efloatseparator}{\hbox{}}}
% \AtBeginTables{\section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\usepackage[x11names,svgnames]{xcolor}
\usepackage{texshade}
\usepackage{tikz}
\usepackage{nameref}
\usepackage{zref-xr,zref-user}
\usepackage{cleveref}
\newenvironment{narrow}[2]{%
  \begin{list}{}{%
      \setlength{\topsep}{0pt}%
      \setlength{\leftmargin}{#1}%
      \setlength{\rightmargin}{#2}%
      \setlength{\listparindent}{\parindent}%
      \setlength{\itemindent}{\parindent}%
      \setlength{\parsep}{\parskip}}%
  \item[]}{\end{list}}
\def\newblock{\hskip}
\newenvironment{paperquote}{%
  \begin{quote}%
     \it
  }%
  {\end{quote}}
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
\newenvironment{enumerate*}%
  {\begin{enumerate}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{enumerate}}
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}
\oddsidemargin 0.0in 
\textwidth 6.5in
\raggedbottom
\clubpenalty = 10000
\widowpenalty = 10000
% make the afill smaller
\renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
\pagestyle{fancy}

@@

\begin{table}
  \begin{tabular}{c c p{3in}}
    \toprule
    Species                       & Collector & Experiment Number & Sample Number(s) \\
    \midrule
    \textit{Ateles fusciceps}     &  & & \\
    \textit{Bos taurus}           & Bob Kreft & & \\
    \textit{Canis familiaris}     &  & & \\
    \textit{Dasypus novemcinctus} &  & & \\
    \textit{Equus caballus}       & \citet{Coleman.ea2010:Structuralannotationofequine} & SRR850299,  SRR850300 \\
    \textit{Loxodonta africana}   & Kurt Benirschke & & \\
    \textit{Homo sapiens}         & Karina Richani, \citet{Hughes.ea2015:Evaluatingintra-andinter-individual} & GSE66622 
                                             & SRR1850945,
                                               SRR1850946, 
                                               SRR1850951, 
                                               SRR1850952, 
                                               SRR1850953, 
                                               SRR1850954, 
                                               SRR1850957, 
                                               SRR1850958, 
                                               SRR1850965, 
                                               SRR1850966, 
                                               SRR1850975, 
                                               SRR1850976, 
                                               SRR1850983, 
                                               SRR1850984, 
                                               SRR1850987, 
                                               SRR1850988, 
                                               SRR1850991, 
                                               SRR1850992, 
                                               SRR1850993, 
                                               SRR1850994, 
                                               SRR1850995, 
                                               SRR1850996, 
                                               SRR1851003, 
                                               SRR1851004, 
                                               SRR1851011, 
                                               SRR1851012 \\
    \textit{Monodelphis domestica} & K. Smith & & \\
    \textit{Mus musculus}         & J. Gonzalez, \cite{Wang.ea2011:surveyfornovelimprinted} & GSE29690 
                                     & SRR243594,
                                       SRR243595,
                                       SRR243596,
                                       SRR243597,
                                       SRR243598,
                                       SRR243599,
                                       SRR243600,
                                       SRR243601,
                                       SRR243602,
                                       SRR243586,
                                       SRR243587,
                                       SRR243588,
                                       SRR243589,
                                       SRR243590,
                                       SRR243591,
                                       SRR243592,
                                       SRR243593\\
    \textit{Nannospalax galili}   &  & GSE68763 & SRR2016467 \\
    \textit{Ovis aries}           & \cite{Archibald.ea2010:sheepgenomereferencesequence} & ERR489144, ERR489145\\
    \textit{Pan paniscus}         &  & \\
    \textit{Spalax carmeli}       &  & GSE68763 & SRR2016467 \\
    \textit{Sus scrofa}           & \cite{Ahanda.ea2012:Predictionofaltered3-} &  SRP014902 & SRR543893 \\
    \bottomrule
  \end{tabular}
  \caption{Species, experiment and species numbers used in the analyses presented in this paper}
  \label{tab:srr_numbers}
\end{table}

>>>>

\documentclass[english,12pt]{article}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{wrapfig}
% \usepackage{txfonts}
\usepackage{acronym}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage[backend=biber,natbib=true,hyperref=true,style=nature,citestyle=numeric-comp,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads,nofighead,notabhead]{endfloat}
% \AtBeginFigures{\section*{Figure Legends}\renewcommand{\efloatseparator}{\hbox{}}}
% \AtBeginTables{\section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\usepackage[x11names,svgnames]{xcolor}
\usepackage{texshade}
\usepackage{tikz}
\usepackage{nameref}
\usepackage{zref-xr,zref-user}
\usepackage{cleveref}
\newenvironment{narrow}[2]{%
  \begin{list}{}{%
      \setlength{\topsep}{0pt}%
      \setlength{\leftmargin}{#1}%
      \setlength{\rightmargin}{#2}%
      \setlength{\listparindent}{\parindent}%
      \setlength{\itemindent}{\parindent}%
      \setlength{\parsep}{\parskip}}%
  \item[]}{\end{list}}
\def\newblock{\hskip}
\newenvironment{paperquote}{%
  \begin{quote}%
     \it
  }%
  {\end{quote}}
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
\newenvironment{enumerate*}%
  {\begin{enumerate}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{enumerate}}
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}
\oddsidemargin 0.0in 
\textwidth 6.5in
\raggedbottom
\clubpenalty = 10000
\widowpenalty = 10000
% make the afill smaller
\renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
\pagestyle{fancy}

@@

\begin{table}
  \begin{tabular}{c p{1.5in} c p{2in}}
    \toprule
    Species                       & Collector & Experiment Number & Sample Number(s) \\
    \midrule
    \textit{Ateles fusciceps}     &  & & \\
    \textit{Bos taurus}           & Bob Kreft & & \\
    \textit{Canis familiaris}     &  & & \\
    \textit{Dasypus novemcinctus} &  & & \\
    \textit{Equus caballus}       & \citet{Coleman.ea2010:Structuralannotationofequine} & GSM1139275 & SRR850299,  SRR850300 \\
    \textit{Loxodonta africana}   & Kurt Benirschke & & \\
    \textit{Homo sapiens}         & Karina Richani, \citet{Hughes.ea2015:Evaluatingintra-andinter-individual} & GSE66622 
                                             & SRR1850945,
                                               SRR1850946, 
                                               SRR1850951, 
                                               SRR1850952, 
                                               SRR1850953, 
                                               SRR1850954, 
                                               SRR1850957, 
                                               SRR1850958, 
                                               SRR1850965, 
                                               SRR1850966, 
                                               SRR1850975, 
                                               SRR1850976, 
                                               SRR1850983, 
                                               SRR1850984, 
                                               SRR1850987, 
                                               SRR1850988, 
                                               SRR1850991, 
                                               SRR1850992, 
                                               SRR1850993, 
                                               SRR1850994, 
                                               SRR1850995, 
                                               SRR1850996, 
                                               SRR1851003, 
                                               SRR1851004, 
                                               SRR1851011, 
                                               SRR1851012 \\
    \textit{Monodelphis domestica} & K. Smith & & \\
    \textit{Mus musculus}         & J. Gonzalez, \citet{Wang.ea2011:surveyfornovelimprinted} & GSE29690 
                                     & SRR243594,
                                       SRR243595,
                                       SRR243596,
                                       SRR243597,
                                       SRR243598,
                                       SRR243599,
                                       SRR243600,
                                       SRR243601,
                                       SRR243602,
                                       SRR243586,
                                       SRR243587,
                                       SRR243588,
                                       SRR243589,
                                       SRR243590,
                                       SRR243591,
                                       SRR243592,
                                       SRR243593\\
    \textit{Nannospalax galili}   &  & GSE68763 & SRR2016467 \\
    \textit{Ovis aries}           & \citet{Archibald.ea2010:sheepgenomereferencesequence} & ERP005642 & ERR489144, ERR489145\\
    \textit{Pan paniscus}         &  & \\
    \textit{Spalax carmeli}       &  & GSE68763 & SRR2016467 \\
    \textit{Sus scrofa}           & \citet{Ahanda.ea2012:Predictionofaltered3-} &  SRP014902 & SRR543893 \\
    \bottomrule
  \end{tabular}
  \caption{Species, experiment and species numbers used in the analyses presented in this paper}
  \label{tab:srr_numbers}
\end{table}
